\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}

### 2014-10-23 pkg/partykit/inst/mloss/mloss2.Rnw
slightly tweaked references to fit on a single page
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@604 255f4249-2263-4417-b1ea-8498779e27a7
A bit of squeezing to optionally include the Acknowledgments on the first four pages:
- If Figure 1 is placed on page 3, then only the references are on page 5.
- If Figure 1 is placed on page 4, the acknowledgments end up on page 5
  as well (but the overall number of pages is not changed).



git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@630 255f4249-2263-4417-b1ea-8498779e27a7

Here, we briefly outline
the most important classes and refer to the vignettes for more details:
\begin{description}
  \item[\class{partysplit}:] Split specification with an integer ID for the
    splitting variable, breakpoint(s), and indexes for the kids.
  \item[\class{partynode}:] Node specification with an integer ID, a
    \class{partysplit}, and a list of kids (if any) that are \class{partynode}
    objects again.
  \item[\class{party}:] Tree specification with a \class{partynode} tree
    along with a \class{data.frame} (which optionally may be empty),
    potentially plus further information about fitted values and so-called
    \class{terms} that allow to preprocess new data for predictions.
\end{description}
All classes have an additional slot for storing arbitrary information at
any level of the tree. This is exploited by \class{constparty}, \class{simpleparty},
and \class{modelparty} which store the observed response, point predictions,
and fitted parametrics models, respectively.
% Extractor functions for the various components of splits, nodes, and trees are provided.

@@

\bibliography{../../vignettes/party.bib}

>>>>

Here, we briefly outline
the most important classes and refer to the vignettes for more details:
\begin{description}
  \item[\class{partysplit}:] Split with integer ID for the
    splitting variable, breakpoint(s), indexes for the kids.
  \item[\class{partynode}:] Node specification with integer ID, a
    \class{partysplit}, and a list of kids (if any) that are \class{partynode}
    objects again.
  \item[\class{party}:] Tree with a recursive \class{partynode}
    and a \class{data.frame} (optionally empty),
    potentially plus information about fitted values and
    \class{terms} allowing to preprocess new data for predictions.
\end{description}
All classes have an additional slot for storing arbitrary information at
any level of the tree. This is exploited by \class{constparty}, \class{simpleparty},
and \class{modelparty} which store the observed response, point predictions,
and fitted parametrics models, respectively.
% Extractor functions for the various components of splits, nodes, and trees are provided.

@@

\bibliography{ref.bib}
